\documentclass[12pt, a4paper]{article}


\title{\textbf{DTL Assignment 2}}
\date{2022-22-11}
\author{Mohit Apte MIS - 112103012}
\begin{document}
\maketitle

\pagenumbering{roman}
\begin{LARGE}
\begin{center}
ORDINARY DIFFERENTIAL EQUATIONS \& MULTIVARIATE CALCULUS
\end{center}
\end{LARGE}
\newpage

\begin{large}
\noindent \textbf {Instructions : }
\end{large}
\begin{itemize}
\item All questions are compulsory.
\item Writing anything on the question paper is not allowed.
\item Mobile phone and programming calculators are strictly prohibited.
\item Exchange/Sharing of stationary, calculator etc. is not allowed.

\end{itemize}


\begin{large}
\begin{enumerate}


\item
Find an equation for the tangent line to the following curve at the point (0,1).
\begin{equation}
2xy^3 + y^4 = 1 + x^3y
\end{equation}

\item
Use the linearization of
\begin{equation}
 f(x) = \sqrt[3]{x} 
 \end{equation}
 at $x=8$ to approximate $\sqrt[3]{8.24}$.

\item
A thermometer reading 10$^{\circ}$C is brought into a room whose
temperature is 27$^{\circ}$C. One minute later the thermometer reading
is 15$^{\circ}$C. How long does it take for the thermometer reading
to become 26.99$^{\circ}$C?

\item
Under what conditions for the constants is the following exact?
Solve it. 
\begin{equation}
(ax + by)dx + (px + qy)dy = 0 
\end{equation}

\item
Find the orthogonal trajectories of the family \begin{equation} y = \sqrt{x+c}
\end{equation}

\item
Solve 
\begin{equation}
xy'' + 2y' + xy = 0
\end{equation}
by reduction of order given that  \begin{equation}
y_1 = \frac{cos(x)}{x} 
\end{equation}is a solution.

\item
If the roots of the auxiliary equation of $2nd$ order homogeneous linear ODE
\begin{equation}
y'' + by' + cy = 0
\end{equation} are real and equal then find the first solution, and the second solution using the method of reduction of order, and hence write the basis.


\end{enumerate}
\begin{center}
\dots END OF QUESTION PAPER \dots
\end{center}
\end{large}


\end{document}
